Counterfactual Training

### 2024-12-19 paper/presenations/slides.qmd
vamos

>>>>

## The Big Oversight

- **Core problem**: `CounterfactualExplanation` objects are *huge*. They store `X` (the input), `y` (the output), etc. in their own memory.
- Can't easily fit `CounterfactualExplanation` objects on cluster memory and pass them around processes. 
- **Good news**: Relatively straightforward to add `FlattenedCE` with gazzilion times lower memory footprint.
